### 2018-10-07 MSc_Marko_Docevski_tekst.tex
Updates from ShareLaTeX

\subsection{Пиално лента}

@@

\cite{Sturm2016} We create data for training our folk-rnn model in the following way. We
remove title fields and ornaments. We remove all transcriptions that have fewer than 7 measures when considering repetitions (to remove contributions that are not complete transcriptions, but transcriptions of suggested endings, variations, etc.). We remove all transcriptions that have more than one meter or key.11 We transpose all remaining transcriptions (23,636) to a key with root C.
We impose a transcription token vocabulary — each token consists of one or more characters — for the following seven types (with examples in parens): meter (“M:3/4”), key (“K:Cmaj”), measure (“:|” and “|1”), pitch (“C” and “c’”),
grouping (“(3”), duration (“2” and “/2”), and transcription (“<s>” and “<\ s>”). 
Our dataset has 4,056,459 tokens, of which 2,816,498 are pitch, 602,673 are du- ration, and 520,290 are measure. A majority of the 23,636 transcriptions consists of 150 tokens or fewer; and 75percent have no more than 190. There are 137 unique tokens, each of which becomes a vocabulary element for our folk-rnn model.

\cite{Yang2017} 
For simplicity, we filtered out MIDI tabs that contain chords other than the 24 basic chord triads (12 major and 12 minor chords). Next, we segmented the remaining tabs every 8 bars, and then pre-processed the melody channel and the chord channel separately, as described below. For melodies, we fixed the smallest note unit to be the sixteenth note, makingw = 16. Specifically, we prolonged notes which have a pause note after them. If the first note of a bar is a pause, we extended the second note to have it played while the bar begins. There are other exceptions such as triplets and shorter notes (e.g. 32nd notes), but we chose to exclude them in this implementation. More- over, for simplicity, we shifted all the melodies into two oc- taves, from C4 to B5, and neglected the velocity of the note events. Although our melodies would use only 24 possible notes after these preprocessing steps, we considered all the 128 MIDI notes (i.e. from C0 to G10) in our symbolic representation. In doing so, we can detect model collaps- ing [12] more easily, by checking whether the model gen- erates notes outside these octaves. As there are no pauses in our data after preprocessing, we do not need a dimension for silence. Therefore, h = 128. For chords, instead of using a 24-dimensional one-hot vector, we found it more efficient to use a chord representa- tion that has only 13 dimensions— the first 12 dimensions for marking the key, and the last for the chord type (i.e. major or minor), as illustrated in Table 2. We pruned the chords such that there is only one chord per bar. After these preprocessing steps, we were left with 526 MIDI tabs (i.e. 4,208 bars). 5 For data augmentation, we circularly shifted the melodies and chords to any of the 12 keys in equal temperament, leading to a final dataset of 50,496 bars of melody and chord pairs for training.

\cite{Tikhonov2017}  1. Spliting the midi tracks and filtering only the desired ones by heuristic. 2. Removed strenght/velocity of the note being played, to focus on the melodic pattern determined by the pitches and temporal parameters of the notes and pauses in between and not performance nuances. 3. In order to make the learning state space denser we have centered the pitches throughout the dataset transposing median pitch of every track to the 4th octave. 4. We also normalized the pauses throughout the dataset in the following manner. For each track we have calculated a median pause. It is only to be expected that absolute majority of the pauses in the track were equal to the median pause multiplied with a rational coefficient (naturally 1/2 and 3/2 were especially popular in the majority of the tracks). We counted all possible pauses in every track and left only the tracks that had 11 different values of the pauses or less (the median + most popular pauses on each side of it). The tracks with higher variety of pauses were not included in the final dataset.
5. Finally to make the input diverse enough we have filtered the tracks with exceedingly small entropy.

@@

A common technique in machine learning is to generate synthetic data as a way to artifi- cially augment the size of the dataset (the number of training examples) in order to improve the learning. In the musical domain, a natural and easy way is transposition, i.e. to trans- pose all examples in all keys21. In addition to artificially augment the dataset, this provides a key (tonality) invariance of all examples and thus makes the examples more generic. This also reduces sparsity in the training data. This transposition technique is for instance used in [61], described in Section 7.7.1.1. An opposed approach is to transpose (align) all ex- amples into a single common key. This has been advocated by [7] to facilitate learning (see Section 7.3.2.1).
4.4.9

\cite{Bretan2016} 3.1 Design of a Musical DBN Autoencoder
In order to analyze and reconstruct a melody we trained a deep autoencoder to encode and decode a single measure of music. This means that our unit (in this scenario) is one measure of music. From the dataset there are roughly 170,000 unique measures. Of these, there are roughly 20,000 unique rhythms seen in the measures. We augment the dataset by manipulating pitches through linear shifts (transpositions) and alterations of the intervals between notes resulting in roughly 80 million unique measures. We augment the dataset by manipulating pitches through linear shifts (transpositions) and alterations
of the intervals between notes. We alter the intervals using two methods: 1) adding a constant value to the original intervals and 2) multiplying a constant value to the intervals. Many different constant values are used and the resulting pitches from the new interval values are superimposed on to the measure’s original rhythms. The new unit is added to the dataset. We restrict the library to measures with pitches that fall into a five octave range (midi notes 36-92). Each measure is transposed up and down a half step so that all instances within the pitch range are covered. The only manipulation performed on the duration values of notes within a measure is the temporal compression of two consecutive measures into a single measure. This “double time" representation effectively increases the number of measures, while leaving the inherent rhythmic structure in tact. After all of this manipulation and augmentation there are roughly 80 million unique measures. We use 60% for training and 40% for testing our autoencoder. The first step in the process is feature extraction and creating a vector representation of the unit. Unit
selection allows for a lossy representation of the events within a measure. As long as it is possible to rank the units it is not necessary to be able to recreate the exact sequence of notes with the autoencoder. Therefore, we can represent each measure using a bag-of-words (BOW) like feature vector. Our features include:
1. counts of note tuples <pitch1, duration1> 2. counts of pitches <pitch1> 3. counts of durations <duration1> 4. counts of pitch class <class1> 5. counts of class and rhythm tuples <class1, duration1> 6. counts of pitch bigrams <pitch1, pitch2>

\chapter{Tools}

@@

@@

@@

>>>>

\subsection{Пиано лента}

@@

По одбирање на податочно множество и репрезентација на истото за потребите на моделот за машинско учење може да се применат оптимизации постапки врз податоците пред извршување на алгоритамо за машинско учење.
Филтрирање на податочно множество, т.е. отстранување на песни, користејќи одреден сет на критериуми за конзистентност може да помогне во подобрување на перформансите на системот. Критериумите можат да бидант нпр:
\begin{itemize}
    \item Сите песни да се напишани во конкретен клуч.
    \item Сите песни да се во одредена метрика.
    \item Сите песни да се во одреден опстег на темпо.
    \item Да нема промена на метрика во песната.
    \item Песните да се комплетни и да нема оштетени или тешки за парсирање или двосмислени елементи.
    \item Нотите да припаѓаат само во одреден тонален распон.
\end{itemize}
Додатно филтрирање може да биде извршено и во рамките на песните. Елементи од изворните податоци кои не носат експлицитно музички податоци обично може да се отстранат без последици. Одредени музички елементи кои вршат модификации на музичките елементи може да се отстранат со последицата дека се губат одредени нуанси на отсвирената музика. Информацијата за интензитет/гласност на отсвирена нота може истотака да се отстрани со загува на нуанса. Доколку има ноти со помало времетраење од времетрање кое ќе го избереме за минимално тогаш пократките може да се отстранат или продолжат. Доколку одлучиме да работиме во ограничен тонален распон, нотите кои спаѓаат надвор од распонот може да ги отстраниме или поместиме внатре во тоналниот распон.

@@

Транспозиција е техника за поместување на множество од ноти за одреден број на полутонови нагоре или надоле со константен интервал. Може да се искористи врз колекција од песни за збогатување на податочното множество. Поместувајки ги сите мелодиски линии во податочното множество во сите можни позиции во тоналниот опсег му овозможува тонална инваријанса (транслациона инваријанса во друг контекст) на моделот за машинско учење и придонесува кон намалување на реткоста (sparsity) на тренинг податоците. Транспозицијата може да се изврши на сите песни кон еден заеднчики основен клуч (пр. \cite{Sturm2016,Tikhonov2017}) или на сите песни кон повеќе (потенцијално сите можни) основни клучеви (пр. \cite{Yang2017,Bretan2016}).

\chapter{Алатки}

Во продолжени ќе дадам краток опис на алатките кои ги искористив за изработка на трудот.

@@

Керас е библиотека за работа со невронски мрежи на високо ниво. Напишана е во Python и може да работи користејќи една од трите најпопуларни библиотеки за машинско учење на ниско ниво: ensorFlow, CNTK или Theano. Приоритет на библиотеката е овозможување на брзо и едноставно креирање на прототипи со користење на машинско учење така што ќе биде едноставна за разбирање и користење прво од човечка страна потоа од машинска. Паралелно процесирачките способности може да се користат на процесор или графичка картичка. Библиотеката е екстремно модуларна, скоро сите елементи кои што се конфигурабилни во невронските мрежи се модули и лесно може да се менуваат. Истите модули се отворени и може да бида проширени или заменети од корисничка страна.

@@

Music21 е Python библиотека за музикологија, развиена на MIT. Намета е да овозможни лесна и детална анализа на музички композиции во симболична форма. Покрај разни музички анализи на постоечка музика, овозможува и модифицирање на истите, како и програматско креирање на музика и музички примероци. Поддржува низа на формати, од кои најзначајни се MIDI и musicxml. Покрај тоа содржи и повеќе колекции на класична музика во јавен домен кои може да се искористат за анализа или за тренирање на моделот за генерирање музика.

@@

Pypianoroll е Python библиотека за работа со пиано лента записи. Подржува работа со записи со една лента или повеќе ленти, како и можности за транспозиција на постоечки пиано ленти. Овозможува и конверзија на MIDI датотеки во пиано лента и обрано, како и графичка визуелизација на пиано лентите.
